### 2022-04-05 paper/Chapters/Conclusion.tex

\chapter{Conclusion} % Main chapter title

\label{Chapter7} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

@@

Should this project be continued in the future, there are multiple ways that additional time and resources could further improve this project.
Similar to the previous section, if more time were available, more testing could be done in various environments to identify any weaknesses in the software that may have gone unnoticed.
After experimenting with streaming over different networks, it would be beneficial to look at polishing the hardware of the project into a self-contained product.
As it stands, it is currently a PCB with peripherals attached that make it cumbersome to carry around.
The groundwork for this has already been laid out in Section \ref{subsec:DesigningHDMI}, with FFC connectors established for one HDMI and one USB port for connection to an embedded screen, and with the footprint of the final PCB and battery fitting within the footprint of the chosen screen.
All that is left is to build an enclosure to house the final product.

>>>>

\chapter{Conclusion}

\label{Chapter7}

@@

Should this project be continued in the future, there are multiple ways that additional time and resources could further improve this project.
The first improvement to make is to fix the issue with USB data described in section \ref{subsec:Manufacturing3}.
This is the only flaw in the hardware preventing it from being considered a completed product.
Similar to the previous section, if more time were available, more testing could be done in various environments to identify any weaknesses in the software that may have gone unnoticed.
After experimenting with streaming over different networks, it would be beneficial to look at polishing the hardware of the project into a self-contained product.
As it stands, it is currently a PCB with peripherals attached that make it cumbersome to carry around.
The groundwork for this has already been laid out in Section \ref{subsec:DesigningHDMI}, with FFC connectors established for one HDMI and one USB port for connection to an embedded screen, and with the footprint of the final PCB and battery fitting within the footprint of the chosen screen.
All that is left is to build an enclosure to house the final product.

### 2022-04-05 paper/Chapters/StateOfTheArt.tex
Tweaks and updates to the hardware sections
Now a nice big sprint can begin. Just need the time
(almost) finish draft of hardware section
Still need to investigate the USB issues and maybe add more detail to the end of the chapter, but other than that I have a couple of questions to resolve then I'm happyish with the chapter

\chapter{State of the Art} % Main chapter title

\label{Chapter3} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

@@

Google Chromoting\todo{Should this chapter be called Chromoting? "Chrome Remote Desktop" is the much more recognizable name though}, implemented publicly as Chrome Remote Desktop, is an open source protocol that enables remote desktop control through any web browser running on the Chromium engine \cite{chromotingBuildInstructions}.
It prioritizes low bandwidth usage and ease of access, allowing easy server install on every major desktop operating system, and enables any web browser or mobile device to act as a client.
By employing the VP8 compression format (Most commonly seen in internet video streaming), Chromoting is able to keep network traffic low by only sending a few full images of the server's screen as keyframes and transmitting motion with compressed partial frames \cite{miniorange_chromoting}.
These partial frames are calculated by the server using the difference between the previous and current frame, allowing the server to only send the difference between the two frames.

@@

\section{Summary}\label{sec:StateOfTheArtSummary}

\todosection

>>>>

\chapter{State of the Art}

\label{Chapter3}

@@

Google Chromoting, implemented publicly as Chrome Remote Desktop, is an open source protocol that enables remote desktop control through any web browser running on the Chromium engine \cite{chromotingBuildInstructions}.
It prioritizes low bandwidth usage and ease of access, allowing easy server install on every major desktop operating system, and enables any web browser or mobile device to act as a client.
By employing the VP8 compression format (Most commonly seen in internet video streaming), Chromoting is able to keep network traffic low by only sending a few full images of the server's screen as keyframes and transmitting motion with compressed partial frames \cite{miniorange_chromoting}.
These partial frames are calculated by the server using the difference between the previous and current frame, allowing the server to only send the difference between the two frames.

@@
